---
title: "Lab 6"
author: "Claire Meuter"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based test

We'll mae our own samples using a psuedo-random generator. We use set.seed which is random number generator 

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)


set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

Say we want to compare these samples. 

```{r}
## way to make a really quick histogram
hist(gp_1)

hist(gp_2)
```
We can just try a T-test
```{r}
t.test(gp_1, gp_2)
```
Meaning of this p-value:if these populations drawn from populations with thte same mean, then there 19.8% chance that 

If these samples were drawn from populations with the same mean (aka same population) the probability of taking to random samples withmeans *at least as diferent* as the sample means we found by random chance (taking into account sprad, n) is 19.8%. We cannot reject the null hypothesis. We fail to reject the null hypothesis. There is no significant difference between group 1 and group 2. 

## Now let's compare this outcome to a rank-based test

## Mann Whitney U unpaired rank-based test
defult of wilcox.test is unpaired

```{r}
mwu <- wilcox.test(gp_1, gp_2) # warning can be ignored

mwu

```
Null hypothesis with rank test is both populations have same rannk

This P-value means that...
If these samples were drawn from populations with the same ranks (medians)  the probability of taking two random samples with ranks *at least as diferent* as the sample rank we found by random chance (taking into account sprad, n) is 28%. 
There is no significant difference in ranks betwen group 1 and group 2 (statistcal summary)

Median scores for group 1 (M = 14) and group 2 ( M = 12) did not differ significantly 

Make sure to send a consistant message about what is responsible analysis 



