---
title: "Lab 6"
author: "Claire Meuter"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based test

We'll mae our own samples using a psuedo-random generator. We use set.seed which is random number generator 

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)


set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

Say we want to compare these samples. 

```{r}
## way to make a really quick histogram
hist(gp_1)

hist(gp_2)
```
We can just try a T-test
```{r}
t.test(gp_1, gp_2)
```
Meaning of this p-value:if these populations drawn from populations with thte same mean, then there 19.8% chance that 

If these samples were drawn from populations with the same mean (aka same population) the probability of taking to random samples withmeans *at least as diferent* as the sample means we found by random chance (taking into account sprad, n) is 19.8%. We cannot reject the null hypothesis. We fail to reject the null hypothesis. There is no significant difference between group 1 and group 2. 

## Now let's compare this outcome to a rank-based test

## Mann Whitney U unpaired rank-based test
defult of wilcox.test is unpaired

```{r}
mwu <- wilcox.test(gp_1, gp_2) # warning can be ignored

mwu

```
Null hypothesis with rank test is both populations have same rannk

This P-value means that...
If these samples were drawn from populations with the same ranks (medians)  the probability of taking two random samples with ranks *at least as diferent* as the sample rank we found by random chance (taking into account sprad, n) is 28%. 
There is no significant difference in ranks betwen group 1 and group 2 (statistcal summary)

Median scores for group 1 (M = 14) and group 2 ( M = 12) did not differ significantly 

Make sure to send a consistant message about what is responsible analysis 

If I do ?wilcox.test in console and then look at values like 
mwu$p.value ... or I can just look at the environment 

If we have more than 2 sample groups we use kruskal.test 

## Linear regression
Now we're starting linear regression (we'll get into this more on Wednesday in lecture)

Simple linear regression (single dependent variable, a simple indepentdent variable)

```{r, include=FALSE}
# Make an exploratory plot of penguin body mass (y-axis) versus flipper length (x-axis)

ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point() + geom_smooth(method = "lm")

# We can set this code chunk to not show up this exploration in the knitted document: do include = FALSE in setup
# Looking at this graph we can relationship between flipper length and body mass- we can use geom_smooth(method = "lm" to see relationship )
```

Find a linear regression model using ordinary least squares describing the relationship between flipper length and body mass for these penguins 
3 pieces:
1. What type of model?
2. What is the relationship to model? (DV ~ IV (s))
3. Where is the data that's used to create this model?


```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)
penguin_lm
```

## When I call up the lm it give the intercept and the flipper length 
y=mx+b
y= body mass
x= flipper length
body mass is equal to 49.7times(flipper length)

49.7 is the slope that describes the flipper length and body mass relationship 
a 1 mm increase in flipper length equals a 49.7 gram change in body mass
-5780.83 grams: when flipper length is zero, this model predicts that the body mass of the penguin would be -5780.83

Because of this it's important to determine in what ranges this model can be realistically used 

### Broom package returns model outputs as tidy data frames

```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

penguin_lm_tidy

broom::glance(penguin_lm)
```


## What if I want to report this model equation in a report? 

```{r}
extract_eq(model = penguin_lm, use_coefs = TRUE)
```

# looks good knitted

```{r}
plot(penguin_lm)
```


